Output Summary

### 2021-11-29 03-post-process/output-plots.Rmd
Update output plots Rmd to reflect new BH parameterization

---
title: "Output Summary"
subtitle: "Multi-Population Model"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
editor_options: 
  chunk_output_type: console
---

@@

```{r dimension-ids}
# the years included by the model
all_yrs = as.numeric(dimnames(jags_data$Pa_obs)[[1]])

# which years are "observable" for at least some quantities?
observable = (jags_data$kmax+1):jags_data$ny

@@

@@

  # extract the posteriors of interest and format for 'posterior' package
  post_sub = as_draws_df(post_subset(post, params))

@@

```{r calculate-mcmc-diagnostics}
# parr recruitment
L1 = "Parr Recruitment"
L2 = c("BH Productivity", "BH Capacity", "Process SD", "Among-pop Correlation", "Parr States")
match = c("alpha", "^beta[", "sig_lPb", "rho_lPb", "^Pb[")
parr_recruit_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

@@

@@

# Initial adult recruitment
L1 = "Initial Adult Recruitment"
L2 = c("Mean", "Realized")
match = c("mu_init_recruits[.]", "^init_recruits[.+,.]")
init_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

@@

# combine diagnostic summaries into one massive table
diags_table = rbind(
  parr_recruit_diags,
  pi_diags,
  phi_Pa_Mb_diags,
  phi_Mb_Ma_diags,
  phi_Ma_O0_diags,
  psi_O1_Rb_diags,
  psi_O2_Rb_diags,
  phi_O0_O1_diags,
  phi_O1_O2_diags,
  phi_Rb_Ra_diags,
  phi_Sb_Sa_diags,
  misc_ocean_surv_diags,
  z_diags,
  init_diags,
  stray_diags
)

@@

# fall trap survival
new = post_subset(post, "Lphi_obs_new_Pa_Ma_dev", TRUE)
obs = post_subset(post, "Lphi_obs_Pa_Ma_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], "fall-mig", pops)
bp = bp[,"fall-mig",]
phi_Pa_Ma_bp = data.frame(
  name = rep("Fall Trap to LGR", 4), pop = pops,
  origin = rep("NOR", 4),   LH_type = rep("Fall Migrants", 4),
  summarize_bp(bp)
)
rownames(phi_Pa_Ma_bp) = NULL

@@

@@

```{r fall-trap-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Pa[.+,LH_type,pop]$", LH_type = i_fall, pop = j)),
               get_obs_ests_log_normal(log(jags_data$Pa_obs[observable,i_fall,j]), jags_data$sig_Pa_obs[observable,i_fall,j]),
               main = pops[j])
}

@@

```{r spring-trap-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Mb[.+,LH_type,origin,pop]$", origin = o_nor, LH_type = i_spring, pop = j)), 
               get_obs_ests_log_normal(log(jags_data$Mb_obs[observable,i_spring,o_nor,j]), jags_data$sig_Mb_obs[observable,i_spring,o_nor,j]),
               main = pops[j])
}

@@

```{r adult-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Ra_tot[.+,pop]$", pop = j)),
               get_obs_ests_log_normal(log(jags_data$Ra_obs[observable,j]), jags_data$sig_Ra_obs[observable,j]),
               main = pops[j])
}

@@

```{r summer-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pb_Ma[.+,pop]", pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pb_Ma[observable,j], jags_data$sig_Lphi_obs_Pb_Ma[observable,j]),
               main = pops[j])
}

@@

```{r fall-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[.+,LH_type,pop]$", LH_type = i_fall, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_fall,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_fall,j]),
               main = pops[j])
}

@@

@@

```{r spring-surv-fit-nor, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[.+,LH_type,origin,pop]$",LH_type = i_spring, origin = o_nor, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j]),
               main = pops[j])
}

@@

```{r spring-surv-fit-hor, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[.+,LH_type,origin,pop]$", LH_type = i_spring, origin = o_hor, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]),
               main = pops[j])
}

@@

```{r hydro-nor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_nor)),
             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_nor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_nor]),
             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"))
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

```{r hydro-hor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_hor)),
             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_hor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_hor]),
             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"))
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

```{r BON-LGR-surv-fit-nor, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[.+,origin]$", origin = o_nor)),
             get_obs_ests_multinomial(cbind(jags_data$LGR_adults[observable,o_nor], jags_data$BON_adults[observable,o_nor] - jags_data$LGR_adults[observable,o_nor]), 1),
             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(NOR)"))
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

```{r BON-LGR-surv-fit-hor, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[.+,origin]$", origin = o_hor)),
             get_obs_ests_multinomial(cbind(jags_data$LGR_adults[observable,o_hor], jags_data$BON_adults[observable,o_hor] - jags_data$LGR_adults[observable,o_hor]), 1),
             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(HOR)"))
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

# containers
x_weir_age_obs = x_carc_age_obs = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
x_weir_origin_obs = x_carc_origin_obs = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))

@@

  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,3,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,4,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,5,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,6,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"))

@@

# for fits to each age, aggregated across origins
weir_comp_fit_plot_age = function(j) {
  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,3,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), ylim = c(0,1))
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}

@@

  plot_tseries(post_summ(post, sub_index("^q_Ra_origin[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_origin_obs[observable,,j], 1), main = TeX("$NOR$"), ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^q_Ra_origin[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_origin_obs[observable,,j], 2), main = TeX("$HOR$"), ylim = c(0,1))
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}
```

@@

plot_f = function(j) {
  par(yaxs = "r")
  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[.+,pop]", pop = j)),
               get_obs_ests_multinomial(cbind(jags_data$carcs_spawned[,j], jags_data$carcs_sampled[,j] - jags_data$carcs_spawned[,j])[observable,], 1),
               main = pops[j], ylim = c(0,1))
  par(mar = c(1.5,1.5,2,0.5), yaxs = "i")

@@

  # fit ordinary least squares version
  ols_fit = fit_fecund_BH(jags_data, pop = j)$BH_fit

>>>>

---
title: "Output Summary"
subtitle: "Multi-Population Model"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "new-BH"
    input: text
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
    input: checkbox
editor_options: 
  chunk_output_type: console
---

@@

```{r dimension-ids}
# the years included by the model
all_yrs = as.numeric(dimnames(jags_data$phi_SL)[[1]])

# which years are "observable" for at least some quantities?
observable = 2:jags_data$ny_obs

# which years are simulated for at least some quantities?
simulated = which(!(all_yrs %in% all_yrs[observable]) & all_yrs > min(all_yrs[observable]))

# which years should be included in time series plots?
if (params$include_sim_years) {
  ts_yrs = c(observable, simulated)
} else {
  ts_yrs = observable
}

# which years can be plotted for SARs? Drop off last kmax years
# since brood year adult returns not complete
sar_yrs = ts_yrs[-((length(ts_yrs) - jags_data$kmax + 1):length(ts_yrs))]

@@

```{r make-diag-post, message = FALSE}
# make a reduced diagnostic posterior: drop out all quantities associated with simulated years
# there is no point in calculating diagnostic summaries for future years
if (length(simulated) > 0) {
  diag_post = post_remove(post, paste0("[", simulated), ask = FALSE)
} else {
  diag_post = post
}
```

@@

  # extract the posteriors of interest and format for 'posterior' package
  post_sub = as_draws_df(post_subset(diag_post, params))

@@

```{r calculate-mcmc-diagnostics}
# parr recruitment
L1 = "Egg-to-Parr Survival"
L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Realized Survival", "Parr States")
match = c("alpha", "^beta[", "mu_beta_per_wul", "sig_lbeta", "sig_Lphi_f_Pb", "rho_Lphi_f_Pb", "^phi_f_Pb[", "^Pb[")
parr_recruit_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

@@

# parr survival from summer to winter tagging
L1 = "Survival From Summer to Winter"
match = c("phi_Pb_Pa[2,.]")
phi_Pb_Pa_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1)))

@@

# Initial adult recruitment
L1 = "Initial Adult Returns"
L2 = c("Age-3", "Age-4", "Age-5")
match = c("Rb\\[[2|3|4],1,1,.\\]", "Rb\\[[2|3|4|5],2,1,.\\]", "Rb\\[[2|3|4|5|6],3,1,.\\]")
init_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[[i]], L1 = L1, L2 = L2[i])))

@@

# combine diagnostic summaries into one massive table
diags_table = rbind(
  parr_recruit_diags,
  pi_diags,
  phi_Pb_Pa_diags,
  phi_Pa_Mb_diags,
  phi_Mb_Ma_diags,
  phi_Ma_O0_diags,
  psi_O1_Rb_diags,
  psi_O2_Rb_diags,
  phi_O0_O1_diags,
  phi_O1_O2_diags,
  phi_Rb_Ra_diags,
  phi_Sb_Sa_diags,
  misc_ocean_surv_diags,
  z_diags,
  init_diags,
  stray_diags
)

@@

# fall & winter trap survival
new = post_subset(post, "Lphi_obs_new_Pa_Ma_dev", TRUE)
obs = post_subset(post, "Lphi_obs_Pa_Ma_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), pops)
bp = cbind(CAT_fall = bp[,"fall-mig","CAT"], CAT_spring = bp[,"spring-mig","CAT"],
           LOS_fall = bp[,"fall-mig","LOS"], LOS_spring = bp[,"spring-mig","LOS"],
           MIN_fall = bp[,"fall-mig","MIN"], MIN_spring = bp[,"spring-mig","MIN"],
           UGR_fall = bp[,"fall-mig","UGR"], UGR_spring = bp[,"spring-mig","UGR"])
phi_Pa_Ma_bp = data.frame(
  name = rep(c("Fall Trap to LGR", "Winter Tagging"), each = 4), pop = rep(pops, 2),
  origin = rep("NOR", 8),   LH_type = rep(c("Fall Migrants", "Spring Migrants"), each = 4),
  summarize_bp(bp)
)
rownames(phi_Pa_Ma_bp) = NULL

@@

## Process Noise Diagnostics

The model assumes mean-zero process noise for all components. That is, the model has an expected value for each component in a given year, and it estimates deviations from this expected value to obtain the realized value in that year. Deviations from the expectation are assumed to be equally likely to be positive or negative for any given year. We can average the process noise components across years to check if it is close to zero. Large deviations from zero in the table below indicate a problem.

```{r get-resids-fn}
# a function to extract the posterior mean of all process model residuals for a single population
get_resids = function(post, j) {

  out = list(
    egg_to_parr_surv = post_summ(post, sub_index("^lPb_resid[.+,pop]", pop = j))["mean",],
    p_fall_mig = post_summ(post, sub_index("^Lpi_resid[.+,pop]", pop = j))["mean",],
    ow_surv_fall = post_summ(post, sub_index("^Lphi_Pa_Mb_resid[.+,LH_type,pop]", pop = j, LH_type = 1))["mean",],
    ow_surv_spring = post_summ(post, sub_index("^Lphi_Pa_Mb_resid[.+,LH_type,pop]", pop = j, LH_type = 2))["mean",],
    toLGR_surv_nor = post_summ(post, sub_index("^Lphi_Mb_Ma_resid[.+,origin,pop]", pop = j, LH_type = 2, origin = 1))["mean",],
    toLGR_surv_hor = post_summ(post, sub_index("^Lphi_Mb_Ma_resid[.+,origin,pop]", pop = j, LH_type = 2, origin = 2))["mean",],
    LGR_to_BON_surv_nor = post_summ(post, sub_index("^Lphi_Ma_O0_resid[.+,origin]", origin = 1))["mean",],
    LGR_to_BON_surv_hor = post_summ(post, sub_index("^Lphi_Ma_O0_resid[.+,origin]", origin = 2))["mean",],
    yr1_ocean_surv = post_summ(post, sub_index("^Lphi_O0_O1_resid[.+,1,pop]", pop = j))["mean",-1],
    age3_mat_nor = post_summ(post, sub_index("^Lpsi_O1_Rb_resid[.+,origin,pop]", origin = 1, pop = j))["mean",],
    age3_mat_hor = post_summ(post, sub_index("^Lpsi_O1_Rb_resid[.+,origin,pop]", origin = 2, pop = j))["mean",],
    age4_mat_nor = post_summ(post, sub_index("^Lpsi_O2_Rb_resid[.+,origin,pop]", origin = 1, pop = j))["mean",],
    age4_mat_hor = post_summ(post, sub_index("^Lpsi_O2_Rb_resid[.+,origin,pop]", origin = 2, pop = j))["mean",],
    BON_to_LGR_surv_nor = post_summ(post, sub_index("^Lphi_Rb_Ra_resid[.+,origin]", origin = 1))["mean",],
    BON_to_LGR_surv_hor = post_summ(post, sub_index("^Lphi_Rb_Ra_resid[.+,origin]", origin = 2))["mean",],
    prespawn_surv = post_summ(post, sub_index("Lphi_Sb_Sa_resid[.+,pop]", pop = j))["mean",]
  )
  out = do.call(cbind, out)
  rownames(out) = NULL
  out
}
```

```{r make-mean-zero-resid-table}
# extract posterior mean residual time series for each population
resids = lapply(1:4, get_resids, post = diag_post)

# convert to array format (list elements become matrix slices)
resids = do.call(abind, append(resids, list(along = 3)))
dimnames(resids)[[3]] = c("CAT", "LOS", "MIN", "UGR")

# calculate the mean of each time series: these should be close to 0
resid_means = t(sapply(1:dim(resids)[2], function(p) colMeans(resids[,p,])))
rownames(resid_means) = dimnames(resids)[[2]]
resid_means = round(resid_means, 3)

# determine the phase of each process model component
is_fw_juvn = rownames(resid_means) %in% c("egg_to_parr_surv", "p_fall_mig", "ow_surv_fall", "ow_surv_spring", "toLGR_surv_nor", "toLGR_surv_hor", "LGR_to_BON_surv_nor", "LGR_to_BON_surv_hor")
is_sw_juvn = stringr::str_detect(rownames(resid_means), "ocean|mat")

# determine the origin of each
is_nor = stringr::str_detect(rownames(resid_means), "nor|egg_to_parr|p_fall|ow_surv")
is_hor = stringr::str_detect(rownames(resid_means), "hor")

# determine the process type: Life History (pi & psi) or Survival (phi)
is_surv = stringr::str_detect(rownames(resid_means), "surv")

# determine the migratory strategy: fall/spring/combined
is_fall = stringr::str_detect(rownames(resid_means), "fall")
is_spring = stringr::str_detect(rownames(resid_means), "spring")

# build ID data frame
resid_IDs = data.frame(
  life_phase = ifelse(is_fw_juvn, "FW Juvenile", ifelse(is_sw_juvn, "SW Juvenile", "FW Adult")),
  type = ifelse(is_surv, "Survival", "Life History"),
  desc = c("Egg-to-Parr", "Strategy Apportionment", "Overwinter", "Overwinter", "Trib to LGR", "Trib to LGR",
           "LGR to BON", "LGR to BON", "Yr1 Ocean", "Age-3 Maturity", "Age-3 Maturity", "Age-4 Maturity", "Age-4 Maturity",
           "BON to LGR", "BON to LGR", "Pre-Spawn"),
  origin = ifelse(is_nor, "NOR", ifelse(is_hor, "HOR", "Combined")), 
  mig_type = ifelse(is_fall, "Fall Migrants", ifelse(is_spring, "Spring Migrants", "Combined"))
)

# combine IDs with mean residual values by population
out = cbind(resid_IDs, resid_means)

# build a kable
kable(out, "html", row.names = FALSE, col.names = c("Life Phase", "Process Type", "Description", "Origin", "Migratory Strategy", colnames(resid_means))) %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
  collapse_rows(1:5)
```

@@

```{r fall-trap-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Pa[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
               get_obs_ests_log_normal(log(jags_data$Pa_obs[observable,i_fall,j]), jags_data$sig_Pa_obs[observable,i_fall,j]),
               yrs = all_yrs[ts_yrs],
               main = pops[j])
}

@@

```{r spring-trap-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Mb[year,LH_type,origin,pop]$", year = ts_yrs, origin = o_nor, LH_type = i_spring, pop = j)), 
               get_obs_ests_log_normal(log(jags_data$Mb_obs[observable,i_spring,o_nor,j]), jags_data$sig_Mb_obs[observable,i_spring,o_nor,j]),
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

@@

```{r adult-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Ra_tot[year,pop]$", year = ts_yrs, pop = j)),
               get_obs_ests_log_normal(log(jags_data$Ra_obs[observable,j]), jags_data$sig_Ra_obs[observable,j]),
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

@@

```{r summer-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pb_Ma[year,pop]", year = ts_yrs, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pb_Ma[observable,j], jags_data$sig_Lphi_obs_Pb_Ma[observable,j]),
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

@@

```{r fall-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_fall,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_fall,j]),
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

@@

### Winter Parr $\rightarrow$ LGR

```{r winter-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = observable, LH_type = i_spring, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_spring,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_spring,j]),
               main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Winter\\,Parr \\rightarrow LGR\\,Survival$"))
```

@@

```{r spring-surv-fit-nor, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_nor, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j]),
               main = pops[j], yrs = all_yrs[ts_yrs])
}

@@

```{r spring-surv-fit-hor, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_hor, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]),
               main = pops[j], yrs = all_yrs[ts_yrs])
}

@@

```{r hydro-nor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_nor)),
             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_nor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_nor]),
             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"),
             yrs = all_yrs[ts_yrs])
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

```{r hydro-hor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_hor)),
             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_hor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_hor]),
             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"),
             yrs = all_yrs[ts_yrs])
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

```{r BON-LGR-surv-fit-nor, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_nor)),
             get_obs_ests_multinomial(cbind(jags_data$LGR_adults[observable,o_nor], jags_data$BON_adults[observable,o_nor] - jags_data$LGR_adults[observable,o_nor]), 1),
             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(NOR)"),
             yrs = all_yrs[ts_yrs])
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

```{r BON-LGR-surv-fit-hor, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_hor)),
             get_obs_ests_multinomial(cbind(jags_data$LGR_adults[observable,o_hor], jags_data$BON_adults[observable,o_hor] - jags_data$LGR_adults[observable,o_hor]), 1),
             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(HOR)"),
             yrs = all_yrs[ts_yrs])
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

# containers
x_weir_age_obs = x_carc_age_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$nk, jags_data$nj))
x_weir_origin_obs = x_carc_origin_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$no, jags_data$nj))

@@

  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
  plot_tseries(post_summ(post, sub_index("^q_Ra[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^q_Ra[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^q_Ra[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^q_Ra[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^q_Ra[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^q_Ra[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"), yrs = all_yrs[ts_yrs])

@@

# for fits to each age, aggregated across origins
weir_comp_fit_plot_age = function(j) {
  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^q_Ra_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^q_Ra_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^q_Ra_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}

@@

  plot_tseries(post_summ(post, sub_index("^q_Ra_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_origin_obs[observable,,j], 1), main = TeX("$NOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^q_Ra_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_origin_obs[observable,,j], 2), main = TeX("$HOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}
```

@@

plot_f = function(j) {
  par(yaxs = "r")
  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[year,pop]", pop = j, year = ts_yrs)),
               get_obs_ests_multinomial(cbind(jags_data$carcs_spawned[,j], jags_data$carcs_sampled[,j] - jags_data$carcs_spawned[,j])[observable,], 1),
               main = pops[j], ylim = c(0,1), yrs = all_yrs[ts_yrs])
  par(mar = c(1.5,1.5,2,0.5), yaxs = "i")

@@
